DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-03 Draft Ped Metrics Example.Rmd
converts st_length() to integer to avoid class of units

# exclude Local Access EASEMENTS & Highway/Freeway
road_df <-st_as_sf(clean_roadcl) %>%
  filter(FCLASS %ni% c(100,110,1,2), RD_LOG_ID > 0) %>%
  mutate(LENGTH = st_length(.))

ncdf <- road_df[!lengths(st_intersects(road_df, cities)), ] %>%
  mutate(LENGTH = st_length(.))

@@

sidewalks_nc <- sidewalks[!lengths(st_intersects(sidewalks, cities)), ]%>% 
  st_as_sf(.) %>%
  filter(WIDTH > 0, LENG_FT > 0) %>%
  mutate(LENGTH = st_length(.),
         TYPE = paste0("Sidewalk: ",WIDTH, " ft"),
         RD_LOG_ID = as.integer(ROADLOGID),
         SEGMENT_ID = as.integer(SEG_ID)) %>%
  select(RD_LOG_ID,SEGMENT_ID,BMP,EMP,SIDE_OF_RO, WIDTH, LENGTH, TYPE)
shoulders_nc <- shoulders[!lengths(st_intersects(shoulders, cities)), ] %>% 
  st_as_sf(.) %>%
  filter(SHLDR_WIDT > 0, SHLDR_SURF == "ACP", DISTANCE_F > 0) %>%
  mutate(LENGTH = st_length(.),
         TYPE = paste0("Paved Shoulder: ", SHLDR_WIDT," ft"),
         RD_LOG_ID = as.integer(ROAD_LOG_I),
         SEGMENT_ID = as.integer(SEG_ID)) %>%
  select(RD_LOG_ID,SEGMENT_ID,BMP,EMP,SIDE_OF_RO, WIDTH = SHLDR_WIDT, LENGTH, TYPE)
nc_sw_sh <- bind_rows(sidewalks_nc, shoulders_nc)

>>>>

# exclude Local Access EASEMENTS & Highway/Freeway
road_df <-st_as_sf(clean_roadcl) %>%
  filter(FCLASS %ni% c(100,110,1,2), RD_LOG_ID > 0) %>%
  mutate(LENGTH = as.integer(st_length(.)))

ncdf <- road_df[!lengths(st_intersects(road_df, cities)), ] %>%
  mutate(LENGTH = as.integer(st_length(.)))

@@

sidewalks_nc <- sidewalks[!lengths(st_intersects(sidewalks, cities)), ]%>% 
  st_as_sf(.) %>%
  filter(WIDTH > 0, LENG_FT > 0) %>%
  mutate(LENGTH = as.integer(st_length(.)),
         TYPE = paste0("Sidewalk: ",WIDTH, " ft"),
         RD_LOG_ID = as.integer(ROADLOGID),
         SEGMENT_ID = as.integer(SEG_ID)) %>%
  select(RD_LOG_ID,SEGMENT_ID,BMP,EMP,SIDE_OF_RO, WIDTH, LENGTH, TYPE)
shoulders_nc <- shoulders[!lengths(st_intersects(shoulders, cities)), ] %>% 
  st_as_sf(.) %>%
  filter(SHLDR_WIDT > 0, SHLDR_SURF == "ACP", DISTANCE_F > 0) %>%
  mutate(LENGTH = as.integer(st_length(.)),
         TYPE = paste0("Paved Shoulder: ", SHLDR_WIDT," ft"),
         RD_LOG_ID = as.integer(ROAD_LOG_I),
         SEGMENT_ID = as.integer(SEG_ID)) %>%
  select(RD_LOG_ID,SEGMENT_ID,BMP,EMP,SIDE_OF_RO, WIDTH = SHLDR_WIDT, LENGTH, TYPE)
nc_sw_sh <- bind_rows(sidewalks_nc, shoulders_nc)

### 2022-10-03 child_single_geo.Rmd
remove extraneous + and move graphing to last chunk
converts st_length() to integer to avoid class of units

```{r} 
library(broom)
this_geo <- st_as_sf(df) %>% filter(tomatch == "{{current_geo}}") 
this_roads <- st_intersection(road_df, st_buffer(this_geo,0))
this_sw_sh <- st_intersection(nc_sw_sh, st_buffer(this_geo,0))

# identified a mislabeled RD_LOG_ID in the sidewalk data for Madrone (as Main)
x <- st_as_sf(this_sw_sh) %>% filter(RD_LOG_ID == 49435 & LENGTH > 1000)
x$RD_LOG_ID <- 43809
# x will have 0 rows if we are not dealing with Manchester

@@

          +

>>>>

```{r} 
library(broom)
this_geo <- st_as_sf(loop_df) %>% filter(tomatch == current_geo) #"{{current_geo}}") 
this_roads <- st_intersection(road_df, st_buffer(this_geo,0))
this_sw_sh <- st_intersection(nc_sw_sh, st_buffer(this_geo,0))

# identified a mislabeled RD_LOG_ID in the sidewalk data for Madrone (as Main)
x <- st_as_sf(this_sw_sh) %>% mutate(LENGTH = as.integer(LENGTH)) %>% filter(RD_LOG_ID == 49435 & LENGTH > 1000)
x$RD_LOG_ID <- 43809
# x will have 0 rows if we are not dealing with Manchester

@@
